### 2022-08-01 manuscript.Rmd

Entropy is a summary measure of posterior class probabilities across classes and individuals.
It ranges from 0 (model classification no better than random chance) to 1 (perfect classification).
As a rule of thumb, values above .80 are deemed acceptable and those approaching 1 are considered ideal.
SHould not be used to select a particural class solution i fclass separability is too low
if the group is too small to be meaningful or to calculate descriptive statistics
could be used to disqualify certain solutions
<!-- Masyn 2013 "entropy was never intended for, nor should it be used for, model selection during the class enumeration process" p. 570 -->
<!-- add content about entropy -->

>>>>

Entropy is a summary measure of posterior class probabilities across classes and individuals.
It ranges from 0 (model classification no better than random chance) to 1 (perfect classification).
As a rule of thumb, values above .80 are deemed acceptable and those approaching 1 are considered ideal.
Entropy should not be used to select a particular class solution. 
An appropriate use of entropy is that it can disqualify certain solutions if class separability is too low 
or if one of the latent classes is too small to be meaningful or to calculate descriptive statistics.

<!-- Masyn 2013 "entropy was never intended for, nor should it be used for, model selection during the class enumeration process" p. 570 -->
<!-- add content about entropy -->
